---
title: "Untitled"
author: "Anne Valder"
date: "2/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# libraries

```{r}
library(readr)
library(readxl)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(tseries)
library(forecast)
library(vars)
```


```{r}
rm(list=ls())
getwd()
setwd("/Users/annevalder/Desktop/UNI /WU WIEN/SoSe_21/MA/R-CODE")
```
# Load all data in (GDP, CCI, Goolge), extension unemployment (statAT), inflation(statAT), uncertainty index (paper Brown et al)

#GDP
```{r}
t_0 <- as.Date("2006-01-01") #Setting start date for the series
t_1 <- as.Date("2021-12-31") #Setting end date for the seriesv
Date <- seq.Date(t_0,t_1,by="quarter")

bigT <- length(Date)
M <- 1
Data   <- matrix(NA,bigT,M)
colnames(Data)  <- c("gdp") 
Data <- as.data.frame(Data)
rownames(Data)  <- as.Date(Date)

Data[(Date%in%gdp_qtrly$QDate),2] <- (GDP_AT$Value)

# abgerufen final am 11.02.2022
#Source: https://data.oecd.org/gdp/quarterly-gdp.htm#indicator-chart
gdp_qtrly <- read.csv("https://raw.githubusercontent.com/anneval/MA_data/main/RData/GDP_oecd.csv")[,6:7]

colnames(gdp_qtrly)[colnames(gdp_qtrly) %in% c("TIME", "Value")] <- c("QDate", "value")
#ts:
gdp_ts <- ts(gdp_qtrly$value[9:71], start=c(2006,1), end = c(2021,3), frequency = 4)

```
#CCI
```{r}
# abgerufen final am 11.02.2022
#Source: https://ec.europa.eu/info/business-economy-euro/indicators-statistics/economic-databases/business-and-consumer-surveys/download-business-and-consumer-survey-data/time-series_en#consumers

cci_mnly <- read.csv2("https://raw.githubusercontent.com/anneval/MA_data/main/RData/CCI_mtly.csv")[253:444,c(1,297)]

colnames(cci_mnly)[colnames(cci_mnly) %in% c("X", "CONS.AT.TOT.COF.BS.M")] <- c("time", "value")
class(cci_mnly$value)
cci_mnly$time <- as.Date(cci_mnly$time)
# transform to quarterly and then do ts:
##1) Temporal Aggregation!
cci_mnly <- arrange(cci_mnly, time)
cci_mnly$QDate <- as.yearqtr(cci_mnly$time)  #### ERROR HERE!
#cci_mnly$QDate <- as.character(CCI_mntly$QDate)
cci_mnly$QDate[cci_mnly$QDate == "2021 Q4"] <- "2021 Q3"
#CI_mntly$QDate <- as.yearqtr(CCI_mntly$QDate)
cci_qtrly <- cci_mnly %>% group_by(QDate) %>%
  summarise_all(mean)

```

# Google
```{r}
# abgerufen: daily update
Google_AT_daily <- read.csv("https://raw.githubusercontent.com/anneval/MA_data/main/raw/at/trendecon_sa.csv")

# transform to quarterly and then do ts:


```


#ADF tests: 
```{r}

```


# transform to ts all,  aggregate data (new gdP!)
# do tests for stationarity
# create one data matrix for Var later
# write down all models  I want todo (Heik models, 4 lags quarterly data, and tests for lag length with arima and VAR models)

# do simple split OOS forecast and expanding OOS forecast, extension LLOCV
# adjust expanding window functions (for Var, arima)

# Robustness different aggregation 
