---
title: "Untitled"
author: "Anne Valder"
date: "2/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# libraries

```{r}
library(readr)
library(readxl)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(tseries)
library(forecast)
library(vars)
```


```{r}
getwd()
setwd("/Users/annevalder/Desktop/UNI /WU WIEN/SoSe_21/MA/R-CODE")
```
# Load all data in (GDP, CCI, Goolge), extension unemployment (statAT), inflation(statAT), uncertainty index (paper Brown et al)

#GDP
```{r}
# abgerufen final am 11.02.2022
#Source: https://data.oecd.org/gdp/quarterly-gdp.htm#indicator-chart
gdp_qtrly <- read.csv("https://raw.githubusercontent.com/anneval/MA_data/main/RData/GDP_oecd.csv")[,6:7]

colnames(gdp_qtrly)[colnames(gdp_qtrly) %in% c("TIME", "Value")] <- c("QDate", "value")

#ts:
gdp_ts <- 
```

#CCI
```{r}
# abgerufen final am 11.02.2022
#Source: https://ec.europa.eu/info/business-economy-euro/indicators-statistics/economic-databases/business-and-consumer-surveys/download-business-and-consumer-survey-data/time-series_en#consumers

cci_mnly <- read.csv2("https://raw.githubusercontent.com/anneval/MA_data/main/RData/CCI_mtly.csv")[253:444,c(1,297)]

colnames(cci_mnly)[colnames(cci_mnly) %in% c("X", "CONS.AT.TOT.COF.BS.M")] <- c("time", "value")

# transform to quarterly and then do ts:



```

# Google
```{r}
# abgerufen: daily update
Google_AT_daily <- read.csv("https://raw.githubusercontent.com/anneval/MA_data/main/raw/at/trendecon_sa.csv")

# transform to quarterly and then do ts:


```


#ADF tests: 
```{r}

```


# transform to ts all,  aggregate data (new gdP!)
# do tests for stationarity
# create one data matrix for Var later
# write down all models  I want todo (Heik models, 4 lags quarterly data, and tests for lag length with arima and VAR models)

# do simple split OOS forecast and expanding OOS forecast, extension LLOCV
# adjust expanding window functions (for Var, arima)

# Robustness different aggregation 
