---
title: "Untitled"
author: "Anne Valder"
date: "2/12/2022"
output: html_document
---
TO DO: runterschreiben was wie und dann seh ich welche Modelle... 

Models I have:

- AR(1) and standard OLS (split data IS and OOS) (6x)
- AR(1) and expanding estimation  (IS and OOS) (6x) - cannot compare to others sample set, correct since incorporate prediction in new train data?
- auto.arima model (lag selection automatic, and 4 (still have to do)) used test and train, explanation on pacf..)
- VAR model (lag selection automatic (and pacf and acf), and 4)

TO DO: 

- forecast aus expanding
- VAR mit test and train!!!! done
- VAR mit expanding... done
- tests on other models as well....! 
- overview of results...! tables (OLS (nur robustness), Expanding, AR, VAR)
- Do new model with consumer Google index statt economic Google index? - initialize new indices..

Question: 
- incorporate further data or not? 
- is expanding window correct?

goal which is best at forecasting GDP! (measured by out of sample accuracy)

Results:
- Which performs best out of sample of all forecasts.. descriptive and plots 
- Compare OeNB, WIfo index 
Robustness:

Dienstag:
Decide train test or whole sample AR and VAR!!! 
PLots in Latex etc results beschreiben which performs best
PLOT in comparison OeNB/ Wifo !!!
### consumer index - robustness forecast mit other google indices?

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# libraries

```{r, include=FALSE}
library(readr)
library(readxl)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(tseries)
library(forecast)
library(vars)
library(GGally)
library(Metrics)
library(caret)
library(collapse)
library(urca)
library(macror) # for latex table adf 
library(xtable) # latex table 
```


```{r}
rm(list=ls())
getwd()
```
# Load all data in (GDP, CCI, Goolge), extension unemployment (statAT), inflation(statAT), uncertainty index (paper Brown et al)

#GDP
```{r}
t_0 <- as.Date("2006-01-01") #Setting start date for the series
t_1 <- as.Date("2021-07-01") #Setting end date for the series
t_2 <- as.Date("2021-12-31")
Date_q <- seq.Date(t_0,t_1,by="quarter")
Date_m <- seq.Date(t_0,t_2,by="month")

bigT <- length(Date_q)
M <- 6
Data   <- matrix(NA,bigT,M)
colnames(Data)  <- c("gdp", "cci", "google","gdp_ts", "cci_ts", "google_ts") 
Data <- as.data.frame(Data)
rownames(Data)  <- as.Date(Date_q)
```


```{r}
# abgerufen final am 11.02.2022
#Source: https://data.oecd.org/gdp/quarterly-gdp.htm#indicator-chart
gdp <- read.csv("https://raw.githubusercontent.com/anneval/MA_data/main/RData/GDP_oecd.csv")[9:71,6:7]

colnames(gdp)[colnames(gdp) %in% c("TIME", "Value")] <- c("QDate", "value")
gdp <- cbind(gdp,Date_q)
#ts:
gdp_ts <- ts(gdp$value, start=c(2006,1), end = c(2021,3), frequency = 4)

Data[(Date_q%in%gdp$Date_q),1] <- gdp$value
Data$gdp_ts <- ts(Data$gdp, start=c(2006,1), end = c(2021,3), frequency = 4)
```
#CCI
```{r, include=FALSE}
# abgerufen final am 11.02.2022
#Source: https://ec.europa.eu/info/business-economy-euro/indicators-statistics/economic-databases/business-and-consumer-surveys/download-business-and-consumer-survey-data/time-series_en#consumers

cci <- read.csv2("https://raw.githubusercontent.com/anneval/MA_data/main/RData/CCI.csv")[253:444,c(1,297)]

colnames(cci)[colnames(cci) %in% c("X", "CONS.AT.TOT.COF.BS.M")] <- c("time", "value")
cci <- cbind(cci,Date_m)
cci <- arrange(cci, Date_m)
cci$Date_q <- as.yearqtr(cci$Date_m) 
cci$Date_q <- as.Date(cci$Date_q)

#cci$Date_q  <- as.character(cci$Date_m)
#cci$Date_q[CCI_mntly$Date_q == "2021 Q4"] <- "2021 Q3"

cci_qtrly <- cci %>% group_by(Date_q) %>%
  summarise_all(mean)

cci_qtrly_63 <- cci_qtrly[1:63,]
Data[(Date_q%in%cci_qtrly_63$Date_q),2] <- (cci_qtrly_63$value)
Data$cci_ts <- ts(Data$cci, start=c(2006,1), end = c(2021,3), frequency = 4)

```

# Google
```{r}
# abgerufen: daily update
Google_AT_daily <- read.csv("https://raw.githubusercontent.com/anneval/MA_data/main/raw/at/trendecon_sa.csv")

# transform to quarterly and then do ts:
Google_AT_daily$time <- as.Date(Google_AT_daily$time)
Google_AT_daily <- arrange(Google_AT_daily, time)
Google_AT_daily$Date_q <- as.yearqtr(Google_AT_daily$time)
Google_AT_daily$Date_q <- as.Date(Google_AT_daily$Date_q)
#Google_AT_daily$QDate  <- as.character(Google_AT_daily$QDate)
#Google_AT_daily$QDate[Google_AT_daily$QDate == "2022 Q1"] <- "2021 Q3"  
#Google_AT_daily$QDate[Google_AT_daily$QDate == "2021 Q4"] <- "2021 Q3"  
Google_AT_qtrly <- Google_AT_daily %>% group_by(Date_q) %>%
  summarise_all(mean)

#rownames(Google_AT_qtrly)  <- as.Date(Date_q)
Google_AT_qtrly_63 <- Google_AT_qtrly[1:63,]
Data[(Date_q%in%Google_AT_qtrly_63$Date_q),3] <- (Google_AT_qtrly_63$value)
Data$google_ts <- ts(Data$google, start=c(2006,1), end = c(2021,3), frequency = 4)
```

# Graphics
```{r}
par(mfrow = c(3,1))

# GDP

ggplot(gdp, aes(x=Date_q, y=value,col = variable)) +
  geom_line(color = "steelblue") +
  theme_light() +
  labs(title = "Quarterly GDP Growth Rate (Q1 2006 - Q3 2021)", x = "Years", y = "Austria's GDP growth (in%)")+
  theme(plot.title = element_text(hjust = 0.5, face ="bold")) +
  scale_x_date(date_labels="%b %y",date_breaks  ="24 month")
  

#CCI

ggplot(cci, aes(x=Date_m, y=value)) +
  geom_line(color = "steelblue") +
  theme_light() +
    labs(title = "Consumer Confidence Austria 2006-2021 (Monthly)", x = "Years", y = "Austria's Consumer Confidence (total)")+
  theme(plot.title = element_text(hjust = 0.5, face ="bold")) +
  scale_x_date(date_labels="%b %y",date_breaks  ="24 month")

# PES - Google

ggplot(Google_AT_daily, aes(x=time, y=value)) +
  geom_line(color = "black") +
  theme_light() +
    labs(title = "Google Trends TrendEcon Daily Indicator AT (2006 - 2021)", x = "Years", y = "Austria's GT daily")+
  theme(plot.title = element_text(hjust = 0.5, face ="bold")) +
  scale_x_date(date_labels="%b %y",date_breaks  ="24 month")
```

# Later graph comparison
```{r}
##### Abilene für comparison abbilden 
ts.plot(ts(Data[,1],frequency = 4, start = c(2006,1)),
          ts(Data[,3],frequency = 4, start = c(2006,1)),
          ts(CCI_qtrly$Value,frequency = 4, start = c(2006,1)),
    col = c("red", "blue","black"),
    xlab = "Year", 
    ylab = "Search Frequency (Wirtschaftskrise)", 
    lwd = 1)
legend("bottomright", c("GDP growth", "PES","CCI"), col=c("red","blue", "black"), lty=c(1),
       inset=c(0,1), xpd=TRUE, horiz=TRUE, bty="n"
       )

## with growth rates of cci...
ts.plot(ts(Data[,1],frequency = 4, start = c(2006,1)),
          ts(Data[,3],frequency = 4, start = c(2006,1)),
          ts(cci_gr$cci_gr,frequency = 4, start = c(2006,1)),
    col = c("red", "blue","black"),
    xlab = "Year", 
    ylab = "Search Frequency (Wirtschaftskrise)", 
    lwd = 1)
legend("bottomright", c("GDP growth", "PES","CCI"), col=c("red","blue", "black"), lty=c(1),
       inset=c(0,1), xpd=TRUE, horiz=TRUE, bty="n"
       )


cci_gr <- ((cci_qtrly$value - lag(cci_qtrly$value))/lag(cci_qtrly$value))  
cci_gr <- as.data.frame(cci_gr)
cci_gr[2:64,]
```
# Dataframes for later models:
```{r}
Data_Var <- Data[,1:3]
Data$gdp_lag <- lag(Data$gdp)

Data_train <- Data[1:44,] # 70%
Data_test <- Data[45:63,] #30%
```

# Correlations:
```{r}
ggpairs(Data[,1:3])
```

# Stationarity: ADF tests 
```{r}
adfgdp <- adf.test(Data$gdp) # stationary
adfcci <- adf.test(Data$cci) # stationary
adfgoogle <- adf.test(Data$google) # not stat # test agao  after remove inlation 
# not stationary since I included inflation... 
adfgdp
adfcci
adfgoogle

adfgdpdiff <- adf.test(diff(Data$gdp))
adf.test(diff(Data$cci))
adf.test(diff(Data$google))
```

#Kpss tests and phillip peron tests:
```{r}
kpss.test(Data$gdp) # stationary
kpss.test(Data$cci) #  stationary at 5%...0.09
kpss.test(Data$google) # stationary

pp.test(Data$gdp) # stationary
pp.test(Data$cci) # not stationary (0.21)
pp.test(Data$google) # stationary
```

Summary:
```{r}
x<-urTable(Data[,1:3], tests = c("adf", "pp", "kpss"), order = 1, file = NULL,
format="latex")
print(xtable(x, type = "latex"), file = "stattests.tex")
```

# ACF and PACF plots: Reasoning stationarity
```{r}
par(mfrow = c(3,1))
acf(Data$gdp)
acf(Data$cci)
acf(Data$google)

par(mfrow = c(3,1))
pacf(Data$gdp)
pacf(Data$cci)
pacf(Data$google)
```

#### Expanding Window estimation

# Expanding window estimation instead of fixed test and train data set (advantage: average over all)
An expanding window works like this: Use the past 100 days worth of data to estimate a regression model.
Use the regression model to predict the stock price 1 day from now. Use all of the observations including the predicted value for tomorrow (i.e. observations 1 through 101) to run a regression model. Use this to predict the stock price 2 days from now. Use all of the observations including the predicted values to run a regression model. Use this to predict the stock price 3 days from now.Repeat this until you have as many observations as you want to predict

```{r}
expanding_window_OLS <- function(data, dep_var, start = 19){ 
  expanding_OLS <- list() # empty vector
  predicted_OLS <- list()
  resid_OLS <- list()
  error_OLS <- c() 
  i <- 0
  for(t in start:nrow(data)){ # go from 19 bis 63
    i <- i+1 # first one is i=1 
    expanding_OLS[[i]] <- lm(formula = model, data = data[1:(t-1),]) # first train is 1:18
    resid_OLS[[i]] <- resid(expanding_OLS[[i]])
    predicted_OLS[i] <- predict(expanding_OLS, newdata = data[t,]) # change here into newdatda for forecast...
    error_OLS[i] <- as.numeric(predicted_OLS[[i]]- data[t,1]) # against original GDP growth 
    Summary_OLS <- list(expanding_OLS,predicted_OLS, resid_OLS,error_OLS)
  }
  return(Summary_OLS)
}
```

# Model 1 Expanding window

```{r, message=FALSE, warning=FALSE}
dep_var <- "gdp"
model = gdp ~ gdp_lag

expanding_OLS1 <- expanding_window_OLS(Data[2:63,], dep_var, start = 19)

#predictions
pred1 <- do.call(rbind.data.frame, expanding_OLS1[[2]]) # NAs wegen lag! 
Date_q_pred <- Date_q[20:63]
colnames(pred1) <- c("value")

pred1 <- as.ts(pred1, start=c(2010,4), end = c(2021,3), frequency = 4)

# Out of Sample error terms----------------------------------------------------------------
error_OLS1 <- expanding_OLS1[[4]]
error_OLS1 <-error_OLS1[!is.na(error_OLS1)]
MAE_OLS_OOS1 <- mean(abs(error_OLS1))
MAE_OLS_OOS1
RMSE_OLS_OOS1  <- sqrt(mean(error_OLS1^2)) 
RMSE_OLS_OOS1
MSE_OLS1 <- mean(error_OLS1^2) 
MSE_OLS1
# IS error terms----------------------------------------------------------------
# IS: If you are forecasting for an observation that was part of the data sample - it is in-sample forecast.
resid_OLS1 <- expanding_OLS1[[3]]
final_resid_OLS1 <- resid_OLS1[[length(resid_OLS1)]]

RMSE_OLS_IS1    <- sqrt(mean(final_resid_OLS1^2))
RMSE_OLS_IS1

# Autocorrelation residuals:
checkresiduals(final_resid_OLS1)
```

# Plot Model 1 against GDP growth
```{r}
plotexp_1 <- ts.plot(ts(Data[20:63,1],frequency = 4, start = c(2010,4),end = c(2021,3)),
          ts(pred1,frequency = 4, start = c(2010,4),end = c(2021,3)),
    col = c("black", "red"),
    xlab = "Year", 
    ylab = "GDP growth (%)", 
    lwd = 1)
legend("bottomleft", c("GDP growth", "AR(1)"), col=c("black","red"), lty=c(1),
        xpd=TRUE, bty="b", cex=0.75
      )
```

# Model 2 Expanding window
```{r, message=FALSE, warning=FALSE}
model = gdp ~ cci
expanding_OLS2 <- expanding_window_OLS(Data, dep_var, start = 19)

pred2 <- do.call(rbind.data.frame, expanding_OLS2[[2]]) 
colnames(pred2) <- c("value")
rownames(pred2) <- Date_q_pred
Date_q_pred <- Date_q[19:63]

pred2 <- as.ts(pred2, start=c(2010,3), end = c(2021,3), frequency = 4)

# Out of Sample error terms----------------------------------------------------------------
error_OLS2 <- expanding_OLS2[[4]]
error_OLS2 <-error_OLS2[!is.na(error_OLS2)]
MAE_OLS_OOS2 <- mean(abs(error_OLS2))
MAE_OLS_OOS2
RMSE_OLS_OOS2   <- sqrt(mean(error_OLS2^2)) 
RMSE_OLS_OOS2
MSE_OLS2 <- mean(error_OLS2^2) 
MSE_OLS2

# IS error terms----------------------------------------------------------------
# IS: If you are forecasting for an observation that was part of the data sample - it is in-sample forecast.
resid_OLS2 <- expanding_OLS2[[3]]
final_resid_OLS2 <- resid_OLS2[[length(resid_OLS2)]]

RMSE_OLS_IS2   <- sqrt(mean(final_resid_OLS2^2))
RMSE_OLS_IS2

# Autocorrelation residuals:
checkresiduals(final_resid_OLS2)
#plot(forecast(pred,h=3))
```

# Plot Model 2 against GDP growth
```{r, message=FALSE, warning=FALSE}
plotexp_2 <- ts.plot(ts(Data[19:63,1],frequency = 4, start = c(2010,3)),
          ts(pred2,frequency = 4, start = c(2010,3)),
    col = c("black", "red"),
    xlab = "Year", 
    ylab = "GDP growth (%)", 
    lwd = 1)
legend("bottomleft", c("GDP growth", "CCI"), col=c("black","red"), lty=c(1),
        xpd=TRUE, bty="b", cex=0.75
      )
```

# Model 3 Expanding window
```{r, message=FALSE, warning=FALSE}
model = gdp ~ google
expanding_OLS3 <- expanding_window_OLS(Data, dep_var, start = 19)

pred3 <- do.call(rbind.data.frame, expanding_OLS3[[2]]) 
pred3
colnames(pred3) <- c("value")
Date_q_pred <- Date_q[19:63]
pred3 <- as.ts(pred3, start=c(2010,3), end = c(2021,3), frequency = 4)

# Out of Sample error terms----------------------------------------------------------------
error_OLS3 <- expanding_OLS3[[4]]
error_OLS3 <-error_OLS3[!is.na(error_OLS3)]
MAE_OLS_OOS3 <- mean(abs(error_OLS3))
MAE_OLS_OOS3
RMSE_OLS_OOS3 <- sqrt(mean(error_OLS3^2)) 
RMSE_OLS_OOS3
MSE_OLS3 <- mean(error_OLS3^2) 
MSE_OLS3

# IS error terms----------------------------------------------------------------
# IS: If you are forecasting for an observation that was part of the data sample - it is in-sample forecast.

resid_OLS3 <- expanding_OLS3[[3]]
final_resid_OLS3 <- resid_OLS3[[length(resid_OLS3)]]

RMSE_OLS_IS3    <- sqrt(mean(final_resid_OLS3^2))
RMSE_OLS_IS3

# Autocorrelation residuals:
checkresiduals(final_resid_OLS3)
```

# Plot Model 3 against GDP growth
```{r}
plotexp_3 <- ts.plot(ts(Data[19:63,1],frequency = 4, start = c(2010,3)),
          ts(pred3,frequency = 4, start = c(2010,3)),
    col = c("black", "red"),
    xlab = "Year", 
    ylab = "GDP growth (%)", 
    lwd = 1)
legend("bottomleft", c("GDP growth", "PES"), col=c("black","red"), lty=c(1),
        xpd=TRUE, bty="b", cex=0.75
      )
```

# Model 4 Expanding window
```{r, message=FALSE, warning=FALSE}

model = gdp ~ gdp_lag + cci
  expanding_OLS4 <- expanding_window_OLS(Data[2:63,], dep_var, start = 19)

#predictions
pred4 <- do.call(rbind.data.frame, expanding_OLS4[[2]]) # NAS wegen lag! 
Date_q_pred <- Date_q[20:63]
colnames(pred4) <- c("value")
pred4 <- as.ts(pred4, start=c(2010,4), end = c(2021,3), frequency = 4)

# Out of Sample error terms----------------------------------------------------------------
error_OLS4 <- expanding_OLS4[[4]]
error_OLS4 <-error_OLS4[!is.na(error_OLS4)]
MAE_OLS_OOS4 <- mean(abs(error_OLS4))
MAE_OLS_OOS4
RMSE_OLS_OOS4  <- sqrt(mean(error_OLS4^2)) 
RMSE_OLS_OOS4
MSE_OLS4 <- mean(error_OLS4^2) 
MSE_OLS4

# IS error terms----------------------------------------------------------------
# IS: If you are forecasting for an observation that was part of the data sample - it is in-sample forecast.
resid_OLS4 <- expanding_OLS4[[3]]
final_resid_OLS4 <- resid_OLS4[[length(resid_OLS4)]]
RMSE_OLS_IS4   <- sqrt(mean(final_resid_OLS4^2))
RMSE_OLS_IS4

# Autocorrelation residuals:
checkresiduals(final_resid_OLS4)
```

# Model 5 Expanding window
```{r, message=FALSE, warning=FALSE}
model = gdp ~ gdp_lag + google
expanding_OLS5 <- expanding_window_OLS(Data[2:63,], dep_var, start = 19)

#predictions
pred5 <- do.call(rbind.data.frame, expanding_OLS5[[2]]) # NAS wegen lag! 
colnames(pred5) <- c("value")
Date_q_pred <- Date_q[20:63]
pred5 <- as.ts(pred5, start=c(2010,4), end = c(2021,3), frequency = 4)

# Out of Sample error terms----------------------------------------------------------------
error_OLS5 <- expanding_OLS5[[4]]
error_OLS5 <-error_OLS5[!is.na(error_OLS5)]
MAE_OLS_OOS5 <- mean(abs(error_OLS5))
MAE_OLS_OOS5
RMSE_OLS_OOS5  <- sqrt(mean(error_OLS5^2)) 
RMSE_OLS_OOS5
MSE_OLS5 <- mean(error_OLS5^2) 
MSE_OLS5
# IS error terms----------------------------------------------------------------
# IS: If you are forecasting for an observation that was part of the data sample - it is in-sample forecast.
resid_OLS5 <- expanding_OLS5[[3]]
final_resid_OLS5 <- resid_OLS5[[length(resid_OLS5)]]

RMSE_OLS_IS5    <- sqrt(mean(final_resid_OLS5^2))
RMSE_OLS_IS5

# Autocorrelation residuals:
checkresiduals(final_resid_OLS5)
```

# Plot Model 4&5 against GDP growth
```{r}
plotexp_5 <- ts.plot(ts(Data[20:63,1],frequency = 4, start = c(2010,4)),
          ts(pred4,frequency = 4, start = c(2010,4)),
          ts(pred5,frequency = 4, start = c(2010,4)),
    col = c("black", "red","blue"),
    xlab = "Year", 
   ylab = "GDP growth (%)", 
    lwd = 1)
legend("bottomleft", c("GDP growth","CCI & AR(1)" ,"PES & AR(1)"), col=c("black","red","blue"), lty=c(1), xpd=TRUE, bty="b",cex=0.75
       )
```

# Model 6 Expanding window
```{r, message=FALSE, warning=FALSE}
model = gdp ~ gdp_lag + cci + google
expanding_OLS6 <- expanding_window_OLS(Data[2:63,], dep_var, start = 19)

#predictions
pred6 <- do.call(rbind.data.frame, expanding_OLS6[[2]]) # NAS wegen lag! 
colnames(pred6) <- c("value")
Date_q_pred <- Date_q[20:63]
pred6 <- as.ts(pred6, start=c(2010,4), end = c(2021,3), frequency = 4)

# Out of Sample error terms----------------------------------------------------------------
error_OLS6 <- expanding_OLS6[[4]]
error_OLS6 <-error_OLS6[!is.na(error_OLS6)]
MAE_OLS_OOS6 <- mean(abs(error_OLS6))
MAE_OLS_OOS6
RMSE_OLS_OOS6  <- sqrt(mean(error_OLS6^2)) 
RMSE_OLS_OOS6
MSE_OLS6 <- mean(error_OLS6^2) 
MSE_OLS6

# IS error terms----------------------------------------------------------------
# IS: If you are forecasting for an observation that was part of the data sample - it is in-sample forecast.
resid_OLS6 <- expanding_OLS6[[3]]
final_resid_OLS6 <- resid_OLS6[[length(resid_OLS6)]]

RMSE_OLS_IS6    <- sqrt(mean(final_resid_OLS6^2))
RMSE_OLS_IS6
# Autocorrelation residuals:
checkresiduals(final_resid_OLS6)
```

# Model 7 Expanding window
```{r, warning=F, message=FALSE}
model = gdp ~ cci + google
expanding_OLS7 <- expanding_window_OLS(Data, dep_var, start = 19)

#predictions
pred7 <- do.call(rbind.data.frame, expanding_OLS7[[2]]) # NAS wegen lag! 
colnames(pred7) <- c("value")
Date_q_pred <- Date_q[19:63]
pred7 <- as.ts(pred7, start=c(2010,3), end = c(2021,3), frequency = 4)

# Out of Sample error terms----------------------------------------------------------------
error_OLS7 <- expanding_OLS7[[4]]
error_OLS7 <-error_OLS7[!is.na(error_OLS7)]
MAE_OLS_OOS7 <- mean(abs(error_OLS7))
MAE_OLS_OOS7
RMSE_OLS_OOS7  <- sqrt(mean(error_OLS7^2)) 
RMSE_OLS_OOS7
MSE_OLS7 <- mean(error_OLS7^2) 
MSE_OLS7
# IS error terms----------------------------------------------------------------
# IS: If you are forecasting for an observation that was part of the data sample - it is in-sample forecast.
resid_OLS7 <- expanding_OLS7[[3]]
final_resid_OLS7 <- resid_OLS7[[length(resid_OLS7)]]

RMSE_OLS_IS7    <- sqrt(mean(final_resid_OLS7^2))
RMSE_OLS_IS7
# Autocorrelation residuals:
checkresiduals(final_resid_OLS7)
```

# Plot Model 6&7 against GDP growth
```{r}
plotexp_7 <- ts.plot(ts(Data[20:63,1],frequency = 4, start = c(2010,3)),
          ts(pred6,frequency = 4, start = c(2010,3)),
          ts(pred7[2:45,],frequency = 4, start = c(2010,3)),
    col = c("black", "red","blue"),
    xlab = "Year", 
    ylab = "GDP growth (%)", 
    lwd = 1)
legend("bottomleft", c("GDP growth","AR(1) & CCI & PES", "CCI & PES"), col=c("black","red","blue"), lty=c(1), xpd=TRUE, bty="b",cex=0.75
       )
```

Summary results expanding window: 
```{r}
comparison_MAE_OOS <- rbind("MAE_OLS_OOS" = MAE_OLS_OOS1,MAE_OLS_OOS2,MAE_OLS_OOS3,MAE_OLS_OOS4,MAE_OLS_OOS5,MAE_OLS_OOS6,MAE_OLS_OOS7)

comparison_RMSE_OOS <- rbind("RMSE_OLS_OOS" = RMSE_OLS_OOS1,RMSE_OLS_OOS2,RMSE_OLS_OOS3,RMSE_OLS_OOS4,RMSE_OLS_OOS5,RMSE_OLS_OOS6,RMSE_OLS_OOS7)

comparison_RMSE_IS <- rbind("RMSE_OLS_IS" = RMSE_OLS_IS1,RMSE_OLS_IS2,RMSE_OLS_IS3,RMSE_OLS_IS4,RMSE_OLS_IS5,RMSE_OLS_IS6,RMSE_OLS_IS7)

 
comparison_OOS <- data.frame(     "RMSE_OOS" = comparison_RMSE_OOS, 
                                  "RMSE_IS" = comparison_RMSE_IS,
                                  "MAE_OOS" = comparison_MAE_OOS)

stargazer::stargazer(comparison_OOS,summary=FALSE)
```

# EXTENSIONS  

## ARIMA MODEL

###Auto Arima 
```{r}
arima <- auto.arima(Data[,"gdp"], trace = TRUE,  ic = c("aic")) #MA(1)
summary(arima) # IS errors
adf.test(arima$residuals)
stargazer::stargazer(arima$var.coef)

forecast_MA1 <-predict(arima,n.ahead = 3)
forecast_MA1$pred
#forecast <- forecast(Data[,"gdp"], model = arima, h = 10)$fitted # We make a forecast three periods ahead and we extract the fitted values from the object forecast.#predict forecast same here h=...
acc_oos_MA1 <-forecast::accuracy(Data$gdp,forecast_MA1$pred) 
future = forecast(arima, h = 3) # same results as predict and nahead but only this way plotting works!
plot(future)
```

Manually ARIMA  
```{r}
arma1 <- arima(Data$gdp, order = c(1,0,1))
ar2ma1 <- arima(Data$gdp, order = c(2,0,1))
ar1 <- arima(Data$gdp, order = c(1,0,0))
ar2 <- arima(Data$gdp, order = c(2,0,0))
ma1 <- arima(Data$gdp, order = c(0,0,1))

AIC <- AIC(arma1, ar2ma1, ar1, ar2,ma1)
BIC<- BIC(arma1, ar2ma1, ar1, ar2,ma1)
ab<- cbind(AIC, BIC)

stargazer::stargazer(arma1,ar2ma1,ar1,ar2,ma1)
```

## Extension since ARMA(1,1) seems best 
```{r}
ARMA_11 <- Arima(Data$gdp, order = c(1,0,1))
summary(ARMA_11)
adf.test(ARMA_11$residuals)
stargazer::stargazer(ARMA_11$var.coef)

forecast_ARMA1 <-predict(ARMA_11,n.ahead = 3)
forecast_ARMA1$pred

acc_oos_ARMA1 <-forecast::accuracy(Data$gdp,forecast_ARMA1$pred) 
future = forecast(ARMA_11, h = 3) # same results as predict and nahead but only this way plotting works!
plot(future)

```
## VAR MODEL

#Manual VAR select

```{r}
library(vars)
var.AIC <- VAR(Data[,4:6],  type="none" , lag.max = 4, ic = c("AIC"))
var.SC <- VAR(Data[,4:6],  type="none" , lag.max = 4, ic = c("SC"))
var.AIC.c <- VAR(Data[,4:6],  type="const" , lag.max = 4, ic = c("AIC")) ## lag 2
var.SC.c <- VAR(Data[,4:6],  type="const" , lag.max = 4, ic = c("SC")) ## lag 1

AIC.woc <- cbind(AIC(var.AIC), BIC(var.AIC)) 
AIC.wc<- cbind(AIC(var.AIC.c), BIC(var.AIC.c)) 
SC.woc <- cbind(AIC(var.SC), BIC(var.SC)) 
SC.wc <- cbind(AIC(var.SC.c), BIC(var.SC.c)) 

MC.table <- rbind(AIC.woc, AIC.wc, SC.woc, SC.wc)
MC.table.names <- rbind("using AIC without constant", "using AIC with constant",
                        "using SC without constant","using SC with constant")  
rownames(MC.table)<- MC.table.names
colnames(MC.table) <- cbind("AIC", "BIC")

print(xtable::xtable(MC.table,caption="Model Choice Results",label="tab:mc"),
      sanitize.text.function=function(UR.table){UR.table},comment=FALSE)


stargazer(VAR_est$varresult)
```

### VAR model Varselect (GDP,PES,CCI) - best expanding model

```{r}
Yselect <- VARselect(Data[,1:3],type = "const")   
#Yselect <- VARselect(Data[,4:6],type = "none") #lag 2      # computes information criteria
  lag <- Yselect$selection[1]  # AiC, Hq auch 2 , SC auch 
lag 

VAR_est <- VAR(y = Data[,c(1,3)], p = lag,type = "const")
summary(VAR_est$varresult$gdp)
forecast::accuracy(VAR_est$varresult$gdp) # IS accuracy

#summary(VAR_est$varresult$gdp)$adj.r.squared
#summary(VAR_est$varresult$cci)$adj.r.squared
#summary(VAR_est$varresult$google)$adj.r.squared
forecast_VAR <- predict(VAR_est,n.ahead =3)  
forecast_VAR
###### OOS accuracy?
acc_oos_VAR <-forecast::accuracy(Data$gdp,forecast_VAR$fcst$gdp) 
plot(forecast_VAR)
stargazer::stargazer(VAR_est$varresult)
```
# Residual analysis
```{r}
sum2 <- data.frame(
  VAR_est$varresult$gdp$residuals,
  VAR_est$varresult$cci$residuals,
  VAR_est$varresult$google$residuals)

adf.test(VAR_est$varresult$gdp$residuals) # stationary
adf.test(VAR_est$varresult$cci$residuals) #stationary
adf.test(VAR_est$varresult$google$residuals)#stationary
```

# Normality test
```{r}
Normtest <- normality.test(VAR_est) # H0: normality
print(Normtest)
plot(Normtest)
```

```{r}
library(car)
durbinWatsonTest(VAR_est$varresult$google)  # Thereby, a small p-value of < 2.2e-16 indicates there is significant autocorrelation remaining in the residuals in the model below.
```
# serial correlation check
```{r}
ser.test <- serial.test(VAR_est) # H0: no serial correlation
ser.test
```

### VAR with GDP AND PES - 2nd best expanding model 

```{r}
Yselect <- VARselect(Data[,c(1,3)],type = "const")   
#Yselect <- VARselect(Data[,4:6],type = "none") #lag 2      # computes information criteria
  lag <- Yselect$selection[1]  # AiC, Hq auch 2 , SC auch 
lag 

VAR_est <- VAR(y = Data[,c(1,3)], p = lag,type = "const")
summary(VAR_est$varresult$gdp)
forecast::accuracy(VAR_est$varresult$gdp) # IS accuracy

#summary(VAR_est$varresult$gdp)$adj.r.squared
#summary(VAR_est$varresult$cci)$adj.r.squared
#summary(VAR_est$varresult$google)$adj.r.squared
forecasts <- predict(VAR_est,n.ahead =3)  
forecasts
###### OOS accuracy?
acc_oos_VAR <-forecast::accuracy(Data$gdp,forecasts$fcst$gdp) 
plot(forecasts)
stargazer::stargazer(VAR_est$varresult)
```

# Residual analysis
```{r}
sum2 <- data.frame(
  VAR_est$varresult$gdp$residuals,
  VAR_est$varresult$cci$residuals,
  VAR_est$varresult$google$residuals)

adf.test(VAR_est$varresult$gdp$residuals) # stationary
adf.test(VAR_est$varresult$cci$residuals) #stationary
adf.test(VAR_est$varresult$google$residuals)#stationary
```

# Normality test
```{r}
Normtest <- normality.test(VAR_est) # H0: normality
print(Normtest)
plot(Normtest)
```

```{r}
library(car)
durbinWatsonTest(VAR_est$varresult$google)  # Thereby, a small p-value of < 2.2e-16 indicates there is significant autocorrelation remaining in the residuals in the model below.
```
# serial correlation check
```{r}
ser.test <- serial.test(VAR_est) # H0: no serial correlation
ser.test
```

# ROBUSTNESS

# Models Heik: Standard OLS (train and test set)
AR(1)
Model 1: $GDP_t = \beta_0 +\beta_1 GDP_{t-1} + \epsilon_t  \qquad  t =1,\dotsc,T$

```{r}
mod1 <- lm(gdp ~ lag(gdp), data = Data_train)
summary(mod1)
#sqrt(mean(mod1$residuals^2)) # IS 
acc_is1 <-forecast::accuracy(mod1)

pred_mod1 <- predict(mod1, Data_test)
pred_mod1
acc_oos1 <-forecast::accuracy(Data_test$gdp,pred_mod1)
acc_oos1

forecast_mod1 <- predict(mod1, n.ahead = 3)
#plot(forecast_mod1)
```
Model 2:  $GDP_t = \beta_0 +\beta_1 CCI_{t} +\epsilon_t \qquad  t =1,\dotsc,T$
```{r}

#Data_cci <- cci_qtrly[,c(1,3)]
#colnames(Data_cci) <- c("time", "cci") kann forecasten mit dereinen observation mehr aber kann nicht evaluaten... no equivalent gdp value
mod2 <- lm(gdp ~ cci, data = Data_train)
summary(mod2)
sqrt(mean(mod2$residuals^2)) # IS 
acc_is2 <-forecast::accuracy(mod2)

#pred_mod2
pred_mod2 <- predict(mod2,Data_test)
#ts.plot(pred_mod2)
#fore <- predict(mod2,newdata = Data_cci) # predict cci ...

acc_oos2 <-forecast::accuracy(Data_test$gdp,pred_mod2)
acc_oos2
#pred_test <- predict(mod2, cci_test)
#mod2$coefficients

```
Model 3:  $GDP_t = \beta_0 +\beta_1 GT_{t,i} +\epsilon_t \qquad  t =1,\dotsc,T \qquad  n =1,\dotsc,N$

```{r}
# do new data set where google all periods
#colnames(Google_AT_qtrly) <- c("Date_q","time","google")
Data_google <- Google_AT_qtrly[,c(1,3)]
colnames(Data_google) <- c("time", "google")

mod3<- lm(gdp ~ google, data = Data_train)
summary(mod3)
sqrt(mean(mod3$residuals^2)) # IS 
acc_is3 <- forecast::accuracy(mod3) # IS accuracy

pred_mod3 <- predict(mod3, Data_test)
#pred_mod3 <- predict(mod3, Google_AT_qtrly[45:65,])
pred_mod3

acc_oos3 <-forecast::accuracy(Data_test$gdp,pred_mod3)
acc_oos3

fore <- predict(newdata = Data_google,mod3)

#ts.plot(fore)
##ts.plot(Google_AT_qtrly$value)
```
Model 4: $GDP_t = \beta_0 +\beta_1 GDP_{t-1} + \beta_2 CCI_{t} + \epsilon_t \qquad  t =1,\dotsc,T$

```{r}
mod4<- lm(gdp ~ lag(gdp) + cci, data = Data_train)
summary(mod4)
sqrt(mean(mod4$residuals^2)) # IS 
acc_is4 <-forecast::accuracy(mod4) # IS accuracy

pred_mod4 <- predict(mod4, Data_test)
pred_mod4

acc_oos4 <-forecast::accuracy(Data_test$gdp,pred_mod4)
acc_oos4
```
Model 5: $GDP_t = \beta_0 +\beta_1 GDP_{t-1} + \beta_2 GT_{t,i} + \epsilon_t \qquad  t =1,\dotsc,T \qquad  n =1,\dotsc,N$

```{r}
mod5<- lm(gdp ~ lag(gdp) + google, data = Data_train)
summary(mod5)
sqrt(mean(mod5$residuals^2)) # IS 
acc_is5 <- forecast::accuracy(mod5) # IS accuracy

pred_mod5 <- predict(mod5, Data_test)
acc_oos5 <-forecast::accuracy(Data_test$gdp,pred_mod5)
acc_oos5

# test stimmt!
#error <- Data_test$gdp - pred_mod5
#error <-error[!is.na(error)]
#RMSE <- sqrt(mean(error^2))
#RMSE
```

Model 6: $GDP_t = \beta_0 +\beta_1 GDP_{t-1} + \beta_2 CCI_{t} + \beta_3 GT_{t,i} + \epsilon_t \qquad  t =1,\dotsc,T \qquad  n =1,\dotsc,N$
```{r}
mod6<- lm(gdp ~ lag(gdp) + cci + google, data = Data_train)
summary(mod6)
sqrt(mean(mod6$residuals^2)) # IS 
acc_is6 <- forecast::accuracy(mod6) # IS 

##OOS
pred_mod6 <- predict(mod6, Data_test)
acc_oos6 <-forecast::accuracy(Data_test$gdp,pred_mod6)
acc_oos6

#predictnew <- predict(mod6,)
```

```{r}
mod7<- lm(gdp ~ cci + google, data = Data_train)
summary(mod7)
sqrt(mean(mod7$residuals^2)) # IS 
acc_is7 <- forecast::accuracy(mod7) # IS 

##OOS
pred_mod7 <- predict(mod7, Data_test)
acc_oos7 <-forecast::accuracy(Data_test$gdp,pred_mod7)
acc_oos7

#predictnew <- predict(mod6,)
```

#Summary results 
# Add model 7
```{r}
stargazer::stargazer(mod1,mod2,mod3,mod4,mod5,mod6, mod7)

comparison_OLS_IS <- rbind("OLS_IS" = acc_is1,acc_is2,acc_is3,acc_is4,acc_is5,acc_is6,acc_is7)
comparison_OLS_OOS <- rbind("OLS_OOS" = acc_oos1,acc_oos2,acc_oos3,acc_oos4,acc_oos5,acc_oos6,acc_oos7)

stargazer::stargazer(comparison_OLS_IS, summary = FALSE,colnames = TRUE)
stargazer::stargazer(comparison_OLS_OOS, summary = FALSE,colnames = TRUE)

```


# Robustness VAR models
#### VAR(2, GDP,PES, CCI) expanding window 

```{r}
# create new dataset!!!.
Data_Var <-flag(Data[1:3], 1:2)
Data_Var <- cbind(Data[,1:3],Data_Var)## all have lag 2.... 

model= gdp ~ L1.gdp +L2.gdp + L1.cci +L2.cci +L1.google + L2.google

  #change "!! dependt on var names form flag.. 

expanding_VAR2 <- expanding_window_OLS(Data_Var[3:63,], dep_var, start = 13) # adjust start???
#predictions
pred_VAR2 <- do.call(rbind.data.frame, expanding_VAR2[[2]]) # NAS wegen lag! 
colnames(pred_VAR2) <- c("value")
rownames(pred_VAR2) <- Date_q_pred[3:51]
Date_q_pred <- Date_q[13:63]

pred_VAR2 <- as.ts(pred_VAR2, start=c(2009,3), end = c(2021,3), frequency = 4)
#ts.plot(pred_VAR2)

### error in and OOS 
error_VAR2 <- expanding_VAR2[[4]]
error_VAR2 <-error_VAR2[!is.na(error_VAR2)]
MAE_VAR2_OOS <- mean(abs(error_VAR2))
MAE_VAR2_OOS
RMSE_VAR2_OOS  <- sqrt(mean(error_VAR2^2)) 
RMSE_VAR2_OOS
MSE_VAR2 <- mean(error_VAR2^2) 
MSE_VAR2
# IS error terms----------------------------------------------------------------
# IS: If you are forecasting for an observation that was part of the data sample - it is in-sample forecast.
resid_VAR2 <- expanding_VAR2[[3]]
final_resid_VAR2 <- resid_VAR2[[length(resid_VAR2)]]

RMSE_VAR2_IS    <- sqrt(mean(final_resid_VAR2^2))
RMSE_VAR2_IS
```

#### VAR(2, GDP,PES) expanding window 

```{r}
# create new dataset!!!.
Data_Var <-flag(Data[c(1,3)], 1:2)
Data_Var <- cbind(Data[,c(1,3)],Data_Var)## all have lag 2.... 

model= gdp ~ L1.gdp +L2.gdp +L1.google + L2.google

  #change "!! dependt on var names form flag.. 

expanding_VAR2 <- expanding_window_OLS(Data_Var[3:63,], dep_var, start = 13) # adjust start???
#predictions
pred_VAR2 <- do.call(rbind.data.frame, expanding_VAR2[[2]]) # NAS wegen lag! 
colnames(pred_VAR2) <- c("value")
rownames(pred_VAR2) <- Date_q_pred[3:51]
Date_q_pred <- Date_q[13:63]

pred_VAR2 <- as.ts(pred_VAR2, start=c(2010,4), end = c(2021,3), frequency = 4)
#ts.plot(pred_VAR2)

### error in and OOS 
error_VAR2 <- expanding_VAR2[[4]]
error_VAR2 <-error_VAR2[!is.na(error_VAR2)]
MAE_VAR2_OOS <- mean(abs(error_VAR2))
MAE_VAR2_OOS
RMSE_VAR2_OOS  <- sqrt(mean(error_VAR2^2)) 
RMSE_VAR2_OOS
MSE_VAR2 <- mean(error_VAR2^2) 
MSE_VAR2
# IS error terms----------------------------------------------------------------
# IS: If you are forecasting for an observation that was part of the data sample - it is in-sample forecast.
resid_VAR2 <- expanding_VAR2[[3]]
final_resid_VAR2 <- resid_VAR2[[length(resid_VAR2)]]

RMSE_VAR2_IS    <- sqrt(mean(final_resid_VAR2^2))
RMSE_VAR2_IS

```

## Robustness Cross Validation instead of expanding window 

```{r}
ctrl <- trainControl(method = "LOOCV")

# lag problem again... easiest prob do to new data frame and add it as a variables
model1_CV <- train(gdp ~ gdp_lag, data = Data[2:63,], method = "lm", trControl = ctrl)
print(model1_CV)
stargazer::stargazer(model1_CV)

model2_CV <- train(gdp ~ cci, data = Data, method = "lm", trControl = ctrl)
print(model2_CV)

model3_CV <- train(gdp ~ google, data = Data, method = "lm", trControl = ctrl)
print(model3_CV)

model4_CV <- train(gdp ~ gdp_lag + cci, data = Data[2:63,], method = "lm", trControl = ctrl)
print(model4_CV)

model5_CV <- train(gdp ~ gdp_lag + google, data = Data[2:63,], method = "lm", trControl = ctrl)
print(model5_CV)

model6_CV <- train(gdp ~ gdp_lag + google + cci, data = Data[2:63,], method = "lm", trControl = ctrl)
print(model6_CV)

model7_CV <- train(gdp ~ google + cci, data = Data, method = "lm", trControl = ctrl)
print(model7_CV)
```

## Further possible Extensions
```{r}
# different data aggregation?
# maybe policy uncertainty index
# unemployment and inflation VAR
```

### OLD 

### VAR(2) manually test and train

```{r}
trainingdata <- ts(Data_train[,1:3], frequency = 4, start = c(2006, 1),end = c(2010,3))
testdata <- ts(Data_train[,1:3], frequency = 4, start = c(2010, 4),end = c(2021,3))

v <- VAR(trainingdata, p=2,type = "const") # change t0 2.!!!
summary(v$varresult$gdp)
p <- predict(v, n.ahead=3)

p$fcst$gdp

ts.plot(p$fcst$gdp)
#res <- residuals(v$varresult$gdp)
#fits <- fitted(v)
#RMSE <- sqrt(mean(res^2))

acc_is_VAR <-forecast::accuracy(trainingdata,v$varresult$gdp$fitted.values) # works!!! validated against 
###aber nicht test dat verwendet???predicted
acc_oos_VAR <-forecast::accuracy(testdata,p$fcst$gdp) # works!!! validated against test dat
#acc_oos_VAR <-forecast::accuracy(testdata,p$fcst$cci)
#acc_oos_VAR <-forecast::accuracy(testdata,p$fcst$google)

```

### OLD version expanding window
```{r message=FALSE, warning=FALSE, include=FALSE}
expanding_window_OLS <- function(data, dep_var, start = 19){ # change to 12 
  expanding_OLS <- list() # empty vector
  predicted_OLS <- list()
  resid_OLS <- list()
  error_OLS <- c() 
  i <- 0
  for(t in start:nrow(data)){#t in 13:51
    i <- i+1
    expanding_OLS[[i]] <- lm(formula = model, data = data[1:(t-1),]) # start at 13-1 so 12! 
    resid_OLS[[i]] <- resid(expanding_OLS[[i]])
    predicted_OLS[[i]] <- stats::predict(expanding_OLS[[i]],newdata = data[t,])#[t,])
    error_OLS[i]  <- as.numeric(predicted_OLS[[i]] - data[t,1]) # anpassen je nach dem welchs
    Summary_OLS <- list(expanding_OLS,predicted_OLS,resid_OLS,error_OLS)
  }
  return(Summary_OLS)
}

# forecast pred on newly data how do i incporpare that??? 

#x <- predict(expanding_OLS[[1]][[51]],Google_AT_qtrly[64:65,]) # used last estimated model ... 

#error_x  <- as.numeric(x - Google_AT_qtrly$google[64:65]) 
#MAE_OLS_OOS <- mean(abs(error_x))
#MAE_OLS_OOS
##RMSE_OLS_OOS    <- sqrt(mean(error_x^2)) 
#RMSE_OLS_OOS
#MSE_OLS <- mean(error_x^2) 
#MSE_OLS

##### apply model to test set

#accuracy(cafe.test$fitted)
#y_pred <- forecast(Data_test[,"gdp"], model = arima, h=3)$fitted # We call the forecast function passing the testing data through the ARIMA model fitted with the training data and we extract the fitted values.
#y_test <- Data_test[,"gdp"]
#sd_test <- sd(y_test)
#RMSE <- rmse(y_test, y_pred)
#MAE <- mae(y_test, y_pred)
#rss <- sum((y_test - y_pred) ** 2)
#tss <- sum((y_test - mean(y_test)) ** 2)
##R_squared <- 1 - rss/tss
#errors <- as.ts(y_test - y_pred)
#adf.test(errors)
```

#ARIMA(2,0,0) expanding estimation - egal weil AR(2) basiert auf Datatrain... 
```{r}
Data$gdp_lag2 <- lag(Data$gdp_lag)

dep_var <- "gdp"
model = gdp ~ gdp_lag + gdp_lag2

expanding_AR2 <- expanding_window_OLS(Data[3:63,], dep_var, start = 13)

#predictions
pred_AR2 <- do.call(rbind.data.frame, expanding_AR2[[2]]) # NAS wegen lag! 
colnames(pred_AR2) <- c("value")
rownames(pred_AR2) <- Date_q_pred[3:51]
Date_q_pred <- Date_q[13:63]

pred_AR2 <- as.ts(pred, start=c(2009,3), end = c(2021,3), frequency = 4)
ts.plot(pred_AR2)

### error in and OOS 
error_AR2 <- expanding_AR2[[4]]
error_AR2 <-error_AR2[!is.na(error_AR2)]
MAE_OOS_AR2 <- mean(abs(error_AR2))
MAE_OOS_AR2
RMSE_OOS_AR2  <- sqrt(mean(error_AR2^2)) 
RMSE_OOS_AR2
MSE_AR2 <- mean(error_AR2^2) 
MSE_AR2
# IS error terms----------------------------------------------------------------
# IS: If you are forecasting for an observation that was part of the data sample - it is in-sample forecast.
resid_AR2 <- expanding_AR2[[3]]
final_resid_AR2 <- resid_AR2[[length(resid_AR2)]]

RMSE_AR2_IS    <- sqrt(mean(final_resid_AR2^2))
RMSE_AR2_IS
```


